### 2022-06-20 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@acf0c1ba63d6594b25eaf195d286af60757f1bb2 🚀

\hypertarget{bats-occurrences}{%
\subsection{Bats occurrences}\label{bats-occurrences}}

\hypertarget{bats-phylogenetic-diversity}{%
\subsection{Bats phylogenetic
diversity}\label{bats-phylogenetic-diversity}}

\hypertarget{bats-compositional-uniqueness}{%
\subsection{Bats compositional
uniqueness}\label{bats-compositional-uniqueness}}

\hypertarget{results-and-discussion}{%
\section{Results and discussion}\label{results-and-discussion}}

@@

>>>>

@@

\newpage

\hypertarget{bat-occurrences}{%
\subsection{Bat occurrences}\label{bat-occurrences}}

\hypertarget{bat-phylogenetic-diversity}{%
\subsection{Bat phylogenetic
diversity}\label{bat-phylogenetic-diversity}}

\hypertarget{bat-compositional-uniqueness}{%
\subsection{Bat compositional
uniqueness}\label{bat-compositional-uniqueness}}
